Untitled

### 2017-07-14 PaperCode.Rmd
Change distrib
Edited distrib so it can adjust to full priced or other prices.

@@

@@

z<- MakeLeaflet(CeredigionDATA)
z

saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )

@@

@@

@@

prices %>%

@@

#P value has an exponential decay
Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()

>>>>

#Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
# BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
#   StructureData()

@@

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))

CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
  StructureData(2:4)

@@

z<- MakeLeaflet(MonmouthDATA)
z
# 
# saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )

@@

Ceredigion has cheaper LUps even though it has areas with high LUP. When investigating I changed the classes to take account of the different pricing levels in the LAD. This made no difference. However re-running the bootstrapping including only A type purchases in the LAD gave the expected result of high LUP prices. What appeared to be happening was a lot of property was being transferred in unsual ways.

@@

CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )

CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )

ValueTtest(CeredBootAB)
ValueTtest(CeredBootA)
ValueTtest(CeredBootAnorm)

CeredBootAB %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootAnorm %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

@@

Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()
